---
title: "Package reference"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Package description 

## MICE
```{r eval=FALSE}
library(mice)
```
* multiple imputation by chained equations
* one stop shop for filling in (imputing) missing data for modelling

### caret
```{r eval=FALSE}
library(caret)
```
* Classification and Regression Training
* ONe of the best packages for model evaluation and tuning
* Full scope for modelling - data partitioning, model selection, plotting, evaluating fit, etc...

### randomForest
```{r eval=FALSE}
library(randomForest)
```
* The standard random forest algorithm package
* Multiple decision trees with random initialization

### rpart
```{r eval=FALSE}
library(rpart)
```
* Recursive partitioning and regression trees
* Several functions to employ decision tree regression and classification models
* Often used for its plotting function which shows you the breakdown of the regression tree

### Party
```{r eval=FALSE}
library(party)
```
* More recursive partitioning
* Includes ensemble methods for model fitting

### nnet
```{r eval=FALSE}
library(nnet)
```
* Basic neural net package
* Only allows 1 hidden layer

### e1071
```{r eval=FALSE}
library(e1071)
```
* Support Vector Machine package

### kernLab
```{r eval=FALSE}
library(kernLab)
```
* Package for kernel based algorithms and models, clustering, svm, PCA, etc
* SVM, kernel feature analysis, dotproduct primitives, ranking algorithm, Gaussian processes

### Igraph
```{r eval=FALSE}
library(igraph)
```
* Network analysis package

### ROCR
```{r eval=FALSE}
library(ROCR)
```
* visualizing the performance of scoring classifiers

### IPRED
```{r eval=FALSE}
library(ipred)
```
* Improved prediction
* Bagging

### RATTLE
```{r eval=FALSE}
library(rattle)
```
* R analytical tool to learn easily
* Provides a number of gui functions to help visualize data

### gbm
```{r eval=FALSE}
library(gbm)
```
* Gradient Boosting Machine
* Better optimisation of classification and regression problems using gradient boost /adaboost algo

### TAU
```{r eval=FALSE}
library(tau)
```
* Text analysis utilitite

### dummy
```{r eval=FALSE}
library(dummy)
## Usage:
cbind(iris[,-5], dummy(iris))
```
* Creates dummy variables from categorical

### glmnet
```{r eval=FALSE}
library(glmnet)
```
* Lasso and Elastic-net Regularized generalized linear models

### More references:
[Computer world article on R data wrangling packages](http://www.computerworld.com/article/2921176/business-intelligence/great-r-packages-for-data-import-wrangling-visualization.html)